---
title: "problem-set-4-AlistairGluck"
author: "Alistair Gluck"
date: "2/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(broom)
library(gt)
library(stringr)
library(lubridate)
library(ggthemes)
```

```{r echo=FALSE}
#reading in the data and insuring that no errors come up
x <- read_csv("ps_4_elections-poll-nc09-3.csv",
              col_types = cols(
                .default = col_character(),
                turnout_scale = col_double(),
                turnout_score = col_double(),
                w_LV = col_double(),
                w_RV = col_double(),
                final_weight = col_double(),
                timestamp = col_datetime(format = "")))
```
#Question 1
```{r, echo = FALSE}
d <- x %>% 
#removing all respondents that did not support the dems
  filter(response == "Dem") %>% 
#counting respondents that met criteria
  nrow()
```
There were `r d` respondents who supported the Democratic candidate.
```{r, echo = FALSE}
ru <- x %>% 
#filtering out Dems and "3"s
  filter(response %in% c("Rep", "Und")) %>%
#grouped similar responses together to facilitate counting
  group_by(response) %>% 
#counted within each group
  count()
#will subtract values in-line with madlib
```
There were `r ru[1,2] - ru[2,2]` more respondents who favored the Republican candidate than who were Undecided.
```{r, echo = FALSE}
gender <- x %>% 
#selecting relevant columns for simplicity
  select(gender, gender_combined) %>% 
#removing all individuals for whom the gender columns matched
  filter(gender != gender_combined) %>% 
#counting up all the non-matching individuals
  count()
```
There are two gender variables (gender and gender_combined). There are `r gender[]` individuals for whom these variables have different values.
```{r, echo = FALSE}
wr <- x %>%
#removing all irrelevant columns
  select(race_eth, file_race_black) %>% 
#first remove all respondents who aren't listed as white in race_eth, then removing all who are white in both columns
  filter(race_eth == "White", file_race_black != "White") %>% 
#tallying the total number of applicable respondents
  count()
```
There are `r wr[]` respondents listed as “White” under race_eth who are not listed as “White” under file_race_black.
```{r, echo = FALSE}
time <- x %>% 
#isolating relevant columns
  select(response, timestamp) %>%
#eliminate all responses that aren't relevant to madlib
  filter(response %in% c("Rep", "Dem")) %>% 
#organize respondents by response
  group_by(response) %>% 
#find the first (minimum) time for each of the two relevant responses
  summarize(min = min(timestamp)) %>% 
#reorganize data into new columns by response
  spread(response, min) %>% 
#create a new difference column that is comprised of the difference in times, rounded to minutes
  mutate(diff = round(Rep - Dem, digits = 0))
```
The first response of Dem came `r time[1,3]` minutes (rounded to the nearest minute) before the first response of Rep.

#Question 2

```{r, echo = FALSE}
x %>% 
#removing irrelevant columns to enable more effective repetitive testing
  select(race_eth, response, final_weight) %>% 
#disinclude non-data points in all columns
  filter(response %in% c("Rep", "Dem", "Und", 3), 
         race_eth != "[DO NOT READ] Don't know/Refused") %>% 
#reorder the races to match the model
  mutate(race_eth = fct_relevel(race_eth, c("White", "Black", "Hispanic", "Asian", "Other")))  %>%
#reorganize by race and by response within that
  group_by(race_eth, response) %>%
#adding up the final weights within each race and response
  summarize(total = sum(final_weight)) %>% 
#create new columns for each response for each race, turn nonexistent values into 0s
  spread(key = response, value = total, fill = 0) %>%
#remove the reorganization to facilitate creation of the table
  ungroup() %>%
#start to create the necessary values to find proportions
  mutate(all = Dem + Rep + Und + `3`) %>%
#next 3 lines are calculating proportions for each response
  mutate(Dem = Dem/all) %>% 
  mutate(Rep = Rep/all) %>% 
  mutate(Und = Und/all) %>%
#remove unnecessary columns
  select(-all, -`3`) %>% 
#change all NA values into 0
  na_if(0) %>% 
#use the gt package as all cool people do
  gt() %>% 
#relabel columns to match model
  cols_label(Dem = "DEM.", Rep = "REP.", Und = "UND.", race_eth = " ") %>% 
#change proportions into percentages with no decimal places
  fmt_percent(columns = vars(Dem, Rep, Und), decimals = 0) %>%
#change the 0 into a dash
  fmt_missing(columns = 4, rows = 4, missing_text = "-")
  
``` 
  
#Question 3
  
```{r, echo = FALSE}
x %>% 
#filter for relevant education levels
  filter(educ %in% c("Bachelors' degree", "Grade school", "Graduate or Professional Degree", "High school", "Some college or trade school")) %>% 
#reorder the different education levels to mirror model
  mutate(educ = fct_relevel(educ, c("Grade school", "High school", "Some college or trade school", "Bachelors' degree", "Graduate or Professional Degree"))) %>% 
#reorganize data by education level
  group_by(educ) %>% 
#begin violin chart, assigning variables in opposite order as one would think, to facilitate coord flip because this bypasses the position dodge
  ggplot(aes(x = educ, y = final_weight)) +
#swap the axes
  coord_flip() +
#input the violin plot
  geom_violin() +
#make individual data visible
  geom_jitter(alpha = .5, size = 1) +
#change to appropriate theme (guess and check)
  theme_gray() +
#Add titles and subtitles and captions to match the model
  labs(title = "More Educated Matter Less in North Carolina 9th", subtitle = "Poll gives more weight to people who are less likely to participate in polls", caption = "New York Times Upshot/Sienna College 2018 live polls") +
#remove label on x (vertical in this case) axis
  xlab(element_blank()) +
#add label to y (horizontal) axis
  ylab("Weight Given to Respondent in Calculating Poll Results")
  
```

#Question 4

```{r, echo = FALSE, message=FALSE}
#create a label function to relabel facets later
labels <- c(Dem = "Democrats", Rep = "Republicans")
x %>% 
#filter out undecideds and people without a reported age range
  filter(ager != "[DO NOT READ] Refused", response %in% c("Dem", "Rep")) %>%
#reorder data according to response and then by age range
  group_by(response, ager) %>% 
#begin bar chart using geom_bar, due to lack of y aesthetic
  ggplot(aes(x = ager, fill = response)) +
#input the bar format
  geom_bar() +
#divide into two graphs side by side to facilitate the viewer getting a sense of the general age makeup of each party's voters
  facet_wrap(~response, labeller = labeller(response = labels)) +
#add in a fun and appropriate theme
  theme_gray() +
#recolor the bars as is consistent with the parties' theme colors
  scale_fill_manual(breaks = c("Dem", "Rep"), values = c("#008FD5", "#FF2700")) +
#Label both axes
  xlab("Age Range of Respondent") +
  ylab("Number of Respondents")
```

#Colleagues
Niel Schrage, Dasha Metropolitansky, 
Study halls with Dillon Smith and Charles Flood
  