---
title: "problem-set-4-AlistairGluck"
author: "Alistair Gluck"
date: "2/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(broom)
library(gt)
library(stringr)
```

```{r echo=FALSE}
x <- read_csv("ps_4_elections-poll-nc09-3.csv",
              col_types = cols(
                .default = col_character(),
                turnout_scale = col_double(),
                turnout_score = col_double(),
                w_LV = col_double(),
                w_RV = col_double(),
                final_weight = col_double(),
                timestamp = col_datetime(format = "")))
```
#Question 1
```{r, echo = FALSE}
d <- x %>% 
  filter(response == "Dem") %>% 
  nrow()
```
There were `r d` respondents who supported the Democratic candidate.
```{r, echo = FALSE}
ru <- x %>% 
  filter(response %in% c("Rep", "Und")) %>%
  group_by(response) %>% 
  count()
```
There were `r ru[1,2] - ru[2,2]` more respondents who favored the Republican candidate than who were Undecided.
```{r}
gender <- x %>% 
  select(gender, gender_combined) %>% 
  isequal()
```
There are two gender variables (gender and gender_combined). There are `r` individuals for whom these variables have different values.
```{r}
wr <- x %>% 
  select(race_eth) %>% 
  filter(race_eth == "White") %>% 
  nrow


```
There are X respondents listed as “White” under race_eth who are not listed as “White” under file_race_black.
```{r}
time <- x %>% 
  select(response, timestamp) %>% 
  filter(response %in% c("Dem", "Rep")) %>% 
  arrange(timestamp) %>% 
  head()
  
```
The first response of Rep came X minutes (rounded to the nearest minute) before the first response of Dem.
#Question 2
```{r}
x %>% 
  select(file_race, race_eth, response, final_weight) %>% 
  filter(response %in% c("Rep", "Dem", "Und"), 
         race_eth %in% c("White", "Black", "Hispanic", "Asian", "Other")) %>% 
  group_by(race_eth, response)
```